### 2014-05-13 doc/ApTranscriptome_manuscript.Rmd
Some changes

Thermal reactionome of a temperate ant species
============================================

@@

```{r load, echo=FALSE, results='hide'}
options(scipen = 1, digits = 3, warn = -1)
load("../ms.RData")
suppressMessages(library(pander))
suppressMessages(library(ggplot2))
```

@@

![Expression (scaled to allow comparisons among genes) for genes in GO category "response to stress"](../results/GO_stress_High.png)

>>>>

---
output:
  pdf_document:
    biblatex: yes
biblio-files: ApTranscriptome.bib
---
Thermal reactionome of a temperate ant species
============================================

@@

```{r load, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
options(scipen = 1, digits = 3)
load("../ms.RData")
library(pander)
library(ggplot2)
```

@@

#![Expression (scaled to allow comparisons among genes) for genes in GO category "response to stress"](../results/GO_stress_High.png)
